An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-15 draft.tex
SoA Outline
Only cloud-container methos

\section{State of the Art} 
\label{soa}

>>>>

\section{State of the Art} 
\label{soa}
Hadoop
    \cite{fazenda2012} 
    FlexGP \cite{FlexGP}, 
    elephant56 \cite{salza2016elephant56,ferrucci2018using}, 
Pool
    SofEA \cite{merelo2012sofea,sofea:cec2012} , 
    EvoSpace \cite{garcia2015evospace},
Volunteer
    evospace-js \cite{garcia2017evospace}
Queue
    Containers \cite{salza2016approach}
    Seamless local and Cloud \cite{leclerc2016seamless}
    Serverless KafKEO \cite{guervos2018introducing}, 
    Docker Orchestation \cite{dziurzanski2020scalable,zhao2019cloud}
